### 2016-04-22 doc/tables/realdata-bc.tex
Updated analyses...

\begin{tabular}{ccccc}
  Reference & Sequences ($n$) & Location & Risk group & Gene \\
  \hline
  \autocite{wang2015targeting} & 173 & Beijing, China & MSM & \textit{pol} \\
  \autocite{cuevas2009hiv} & 287 & Basque Country, Spain & mixed & \textit{pol} \\
  \autocite{novitsky2013phylogenetic} & \multirow{2}{*}{180} &
  \multirow{2}{*}{Mochudi, Botswana} & \multirow{2}{*}{mixed} &
  \multirow{2}{*}{\textit{env}} \\ \autocite{novitsky2014impact} \\
  \autocite{li2015hiv} & 280 & Shanghai, China & MSM & \textit{pol} \\
  \autocite{niculescu2015recent} & 136 & Romaina & IDU & \textit{pol} \\
  \hline
\end{tabular}

>>>>

\begin{tabular}{ccccc}
  Reference & Sequences ($n$) & Location & Risk group & Gene \\
  \hline
  \textcite{wang2015targeting} & 173 & Beijing, China & MSM & \textit{pol} \\
  \textcite{cuevas2009hiv} & 287 & Basque Country, Spain & mixed & \textit{pol} \\
  \textcite{novitsky2013phylogenetic} & \multirow{2}{*}{180} &
  \multirow{2}{*}{Mochudi, Botswana} & \multirow{2}{*}{HET} &
  \multirow{2}{*}{\textit{env}} \\ \textcite{novitsky2014impact} \\
  \textcite{li2015hiv} & 280 & Shanghai, China & MSM & \textit{pol} \\
  \textcite{niculescu2015recent} & 136 & Romania & IDU & \textit{pol} \\
  unpublished & 399 & British Columbia, Canada & IDU & \textit{pol} \\
  \hline
\end{tabular}
